---
title: "Survival analysis"
author: "Hermela Shimelis"
date: today
format:
  html:
    code-fold: true
    css: custom.css
editor: 
  markdown: 
    wrap: 72
---

## Data: Survival after chemotherapy for Stage B/C colon cancer

### The data was identified from survival R package

### Description

These are data from one of the first successful trials of adjuvant
chemotherapy for colon cancer. Levamisole is a low-toxicity compound
previously used to treat worm infestations in animals; 5-FU is a
moderately toxic (as these things go) chemotherapy agent. There are two
records per person, one for recurrence and one for death.

The purpose of this project is to compare survival between the untreated
(Obs) group vs those treated with amisole (Lev), or amisole + 5-FU.

Column names:

|           |                                                                                   |
|:-----------------|:-----------------------------------------------------|
| id:       | id                                                                                |
| study:    | 1 for all patients                                                                |
| rx:       | Treatment - Obs(ervation), Lev(amisole), Lev(amisole)+5-FU                        |
| sex:      | 1=male                                                                            |
| age:      | in years                                                                          |
| obstruct: | obstruction of colon by tumour                                                    |
| perfor:   | perforation of colon                                                              |
| adhere:   | adherence to nearby organs                                                        |
| nodes:    | number of lymph nodes with detectable cancer                                      |
| time:     | days until event or censoring                                                     |
| status:   | censoring status                                                                  |
| differ:   | differentiation of tumour (1=well, 2=moderate, 3=poor)                            |
| extent:   | Extent of local spread (1=submucosa, 2=muscle, 3=serosa, 4=contiguous structures) |
| surg:     | time from surgery to registration (0=short, 1=long)                               |
| node4:    | more than 4 positive lymph nodes                                                  |
| etype:    | event type: 1=recurrence,2=death                                                  |
|           |                                                                                   |

```{r}
#| echo: true
#| message: false

# Load library
library(dplyr)
library(survival)
library(janitor)
library(magrittr)

```

```{r}
#| echo: true
#| message: false

#Load data
colon <- as_tibble(colon)
head(colon)
```

Since the current analysis is focused on survival, create a new variable
for recurrence time. This will create a data table with one row per
individual.

```{r}
colon_surv <- colon%>%filter(etype == 2) 

# Identify participants with outome = death (not censored)
colon_surv$death <- if_else(colon_surv$status == 1, 0, 1) 

```

Identify participants who had recurrence. Identify those not censorred
for recurrence event. Filter event type = 1 (recurrence), status = 0
(not censored).

```{r}
recurrence <- colon%>%filter(etype == 1 & status == 0)%>%select(id)
recurrence <- recurrence%>%mutate(recurrence = 1) # list of patients with recurrence


colon_surv <- colon_surv%>%merge(recurrence, by = "id", all.x = TRUE)
colon_surv$recurrence[is.na(colon_surv$recurrence)] <- 0

```

## I. Exploratory data analysis

**Check missing values**

```{r}

na_counts <- sapply(colon_surv, function(x)sum(is.na(x)))
na_counts

# replace NAs with mode
table(colon_surv$differ)
mode(colon_surv$differ)
median(colon_surv$nodes, na.rm= TRUE)

colon_surv$differ <- if_else(is.na(colon_surv$differ), 2,colon_surv$differ)
colon_surv$nodes <- if_else(is.na(colon_surv$nodes), 2,colon_surv$nodes)
```

**Insight:** only nodes and differ columns have NA values. Replacing the
23 NAs in differ column with mode, and replace NAs in nodes with median.

**Evaluate continuous variables**

```{r}
#| echo: true
#| message: false

# age
hist(colon_surv$age)
hist(colon_surv$nodes)
hist(colon_surv$time)


```

**Insight:** Age is normally distribute. Number of nodes is skewed to
the right. Time is fairly normally distributed with most the individuals
had event time between 500-3000 days.

Evaluate nodes column to investigate outliers

```{r}
t <- colon_surv%>%filter(node4 ==1) # samples with more than positive lymph nodes
hist(t$nodes) 

```

**Insight:** samples with greater than 4 lymph nodes have less than 5
count in nodes column, so the two columns are not consistent. Therefore,
nodes column will not be used for further analysis.

**Evaluate categorical variables**

```{r }
#| echo: true
#| message: false
 
summary_table <- colon_surv%>%summarise(count =n(),
                                        male = sum(sex), 
                                                       median_age = median(age),
                                                       ct_perforation = sum(perfor),
                                                       ct_adherence_nerby_organ = sum(adhere),
                                                       ct_death = sum(death))

summary_table
```

**Insight:** Total number of participants: 929. About half of the
participants are male and about half were censored, while the other half
died.

```{r}

colon_surv <- colon_surv%>%mutate(differentiation = case_when(differ == 1 ~ "well",
                                                              differ == 2 ~ "moderate",
                                                              differ == 3 ~ "poor"),
                                  local_spread = case_when(extent == 1 ~ "submucosa",
                                                           extent == 2 ~ "muscle",
                                                           extent == 3 ~ "serosa",
                                                           extent == 4 ~ "contiguous"),
                                  surg_to_reg_time = case_when(surg == 0~ "short",
                                                               surg == 1 ~ "long"))



```

**Frequency tables for categorical variables**

```{r}
# frequency tables for categorical variables
# Tumor differentiation
colon_surv %>% 
  tabyl(differentiation, rx) %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 1) %>% 
  adorn_ns()

# extent of local spread
colon_surv %>% 
  tabyl(local_spread, rx) %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 1) %>% 
  adorn_ns()

# colum obstruction
colon_surv %>% 
  tabyl(obstruct, rx) %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 1) %>% 
  adorn_ns()


# colon perforation
colon_surv %>% 
  tabyl(perfor, rx) %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 1) %>% 
  adorn_ns()

# Adherance to nearby organs
colon_surv %>% 
  tabyl(adhere, rx) %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 1) %>% 
  adorn_ns()

# extent of local tumor spread
colon_surv %>% 
  tabyl(local_spread, rx) %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 1) %>% 
  adorn_ns()

# More than 4 lymph nodes with cancer
colon_surv %>% 
  tabyl(node4, rx) %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 1) %>% 
  adorn_ns()

# Recurrence
colon_surv %>% 
  tabyl(recurrence, rx) %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 1) %>% 
  adorn_ns()

# time from surgery to registration
colon_surv %>% 
  tabyl(surg, rx) %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 1) %>% 
  adorn_ns()
```

\
**Summary statistics grouped by treatment**

```{r #| echo: true#| message: false}

summary_table <- colon_surv%>%group_by(rx)%>%summarise(count =n(),
                                                       male = sum(sex),
                                                       median_age = median(age),
                                                       ct_perforation = sum(perfor),
                                                       ct_adherence_nerby_organ = sum(adhere),
                                                       ct_death = sum(death),
                                                       perc_male = (male/count)*100,
                                                       iqr_age = IQR(age))
summary_table

g <- colon_surv%>%filter(rx == "Lev+5FU")
summary(g$age)
```

**Insight:** Each treatment group had about 300 participants. Median
age, number of participants with perforation and adherence are similar
between the three groups. Whereas the total number of death are higher
in the Lev+5FU group.

## II. Table 1: Description of the study population

```{=html}
<style type="text/css">
.tg  {border-collapse:collapse;border-spacing:0;}
.tg td{border-color:black;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;
  overflow:hidden;padding:10px 5px;word-break:normal;}
.tg th{border-color:black;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;
  font-weight:normal;overflow:hidden;padding:10px 5px;word-break:normal;}
.tg .tg-bobw{font-weight:bold;text-align:center;vertical-align:bottom}
.tg .tg-7zrl{text-align:left;vertical-align:bottom}
.tg .tg-8d8j{text-align:center;vertical-align:bottom}
.tg .tg-j6zm{font-weight:bold;text-align:left;vertical-align:bottom}
</style>
```
|                                             |                            | Observation (%) | Amisole (%)  | Amisole + 5-FU (%) |
|----------------|--------------|--------------|--------------|--------------|
|                                             |                            | N=315           | N=310        | N=304              |
| Demographics                                |                            |                 |              |                    |
|                                             | Male                       | 166 (52.3)      | 177 (57.1)   | 141                |
|                                             | Median age (years) \[IQR\] | 60 \[53,68\]    | 61 \[53,69\] | 61 \[52,70\]       |
| Cancer characterstics                       |                            |                 |              |                    |
|                                             | Colon obstruction          | 63 (20.0)       | 63 (20.3)    | 54 (17.8)          |
|                                             | Colon perforation          | 9 (2.9)         | 10 (3.2)     | 8 (2.6)            |
|                                             | Adherence to nearby organs | 47 (14.9)       | 49 (15.8)    | 39 (12.8)          |
| Differentiation of tumor                    |                            |                 |              |                    |
|                                             | Well                       | 27 (8.6)        | 37 (11.9)    | 29 (9.5)           |
|                                             | Moderate                   | 236 (74.9)      | 229 (73.9)   | 221 (72.7)         |
|                                             | Poor                       | 52 (16.5)       | 44 (14.2)    | 54 (17.8)          |
| Extent of local spread                      |                            |                 |              |                    |
|                                             | Contiguous                 | 20 (6.3)        | 12 (3.9)     | 11 (3.6)           |
|                                             | Muscle                     | 38 (12.1)       | 36 (11.6)    | 32 (10.5)          |
|                                             | Serosa                     | 249 (79.0)      | 259 (83.5)   | 251 (82.6)         |
|                                             | Submucosa                  | 8 (2.5)         | 3 (1.0)      | 10 (3.3)           |
| More than 4 lymh nodes with cancer          | Yes                        | 87 (27.6)       | 89 (28.7)    | 79 (26.0)          |
| Recurrence (%)                              | Yes                        | 138 (43.8)      | 138 (44.5)   | 185 (60.9)         |
| Short time from surgery to registration (%) | Yes                        | 91 (28.9)       | 80 (25.8)    | 76 (25.0)          |
