---
title: "EDA and Methods"
author: "Hermela Shimelis"
date: today
format:
  html:
    code-fold: true
    css: custom.css
bibliography: references.bib # file contains bibtex for references
#always_allow_html: true # this allows to get PDF with HTML features
csl: ieee.csl
self-contained: true
execute: 
  warning: false
  message: false
editor: 
  markdown: 
    wrap: 72    
---

## Data: Survival after chemotherapy for Stage B/C colon cancer

### The data was identified from survival R package

### Description

These are data from one of the first successful trials of adjuvant
chemotherapy for colon cancer. Levamisole is a low-toxicity compound
previously used to treat worm infestations in animals; 5-FU is a
moderately toxic (as these things go) chemotherapy agent. There are two
records per person, one for recurrence and one for death.

The purpose of this project is to compare survival between the untreated
(Obs) group vs those treated with amisole (Lev), or amisole + 5-FU.

Column names:

+:----------------------+:------------------------------------------+
| id:                   | id                                        |
+-----------------------+-------------------------------------------+
| study:                | 1 for all patients                        |
+-----------------------+-------------------------------------------+
| rx:                   | Treatment - Obs(ervation), Lev(amisole),  |
|                       | Lev(amisole)+5-FU                         |
+-----------------------+-------------------------------------------+
| sex:                  | 1=male                                    |
+-----------------------+-------------------------------------------+
| age:                  | in years                                  |
+-----------------------+-------------------------------------------+
| obstruct:             | obstruction of colon by tumour            |
+-----------------------+-------------------------------------------+
| perfor:               | perforation of colon                      |
+-----------------------+-------------------------------------------+
| adhere:               | adherence to nearby organs                |
+-----------------------+-------------------------------------------+
| nodes:                | number of lymph nodes with detectable     |
|                       | cancer                                    |
+-----------------------+-------------------------------------------+
| time:                 | days until event or censoring             |
+-----------------------+-------------------------------------------+
| status:               | censoring status                          |
+-----------------------+-------------------------------------------+
| differ:               | differentiation of tumour (1=well,        |
|                       | 2=moderate, 3=poor)                       |
+-----------------------+-------------------------------------------+
| extent:               | Extent of local spread (1=submucosa,      |
|                       | 2=muscle, 3=serosa, 4=contiguous          |
|                       | structures)                               |
+-----------------------+-------------------------------------------+
| surg:                 | time from surgery to registration         |
|                       | (0=short, 1=long)                         |
+-----------------------+-------------------------------------------+
| node4:                | more than 4 positive lymph nodes          |
+-----------------------+-------------------------------------------+
| etype:                | event type: 1=recurrence,2=death          |
+-----------------------+-------------------------------------------+
|                       |                                           |
+-----------------------+-------------------------------------------+

```{r}
#| echo: true
#| message: false
#| warning: false

# Load library
library(dplyr)
library(survival)
library(janitor)
library(magrittr)
library(car)
library(ggplot2)
library(tidyverse)
library(broom)
library(MASS)
library(boot)

#print(citation("boot"), bibtex=TRUE)

```

```{r}
#| echo: true
#| message: false

#Load data
colon <- as_tibble(colon)
head(colon)
```

Since the current analysis is focused on survival, filter data to death
as the event type. This will create a data table with one row per
individual.

```{r}
colon_surv <- colon%>%filter(etype == 2) 

# Identify participants with outome = death (not censored)
colon_surv$death <- if_else(colon_surv$status == 1, 1, 0) 

```

Identify participants who had recurrence. Identify those not censored
for recurrence event. Filter event type = 1 (recurrence), status = 1.

```{r}
recurrence <- colon%>%filter(etype == 1 & status == 1)%>%dplyr::select(id)
recurrence <- recurrence%>%mutate(recurrence = 1) # list of patients with recurrence


colon_surv <- colon_surv%>%merge(recurrence, by = "id", all.x = TRUE)
colon_surv$recurrence[is.na(colon_surv$recurrence)] <- 0

```

## I. Exploratory data analysis

**Check missing values**

```{r}

na_counts <- sapply(colon_surv, function(x)sum(is.na(x)))
na_counts

# replace NAs with mode
table(colon_surv$differ)
mode(colon_surv$differ)
median(colon_surv$nodes, na.rm= TRUE)

colon_surv$differ <- if_else(is.na(colon_surv$differ), 2,colon_surv$differ)
colon_surv$nodes <- if_else(is.na(colon_surv$nodes), 2,colon_surv$nodes)
```

**Insight:** only nodes and differ columns have NA values. Replacing the
23 NAs in differ column with mode, and replace NAs in nodes with median.

**Evaluate continuous variables**

```{r}
#| echo: true
#| message: false

# age
hist(colon_surv$age)
hist(colon_surv$nodes)
hist(colon_surv$time)


```

**Insight:** Age is normally distribute. Number of nodes is skewed to
the right. Time is fairly normally distributed with most the individuals
had event time between 500-3000 days.

Evaluate nodes column to investigate outliers

```{r}
t <- colon_surv%>%filter(node4 ==1) # samples with more than positive lymph nodes
hist(t$nodes) 


```

**Insight:** samples with greater than 4 lymph nodes have less than 5
count in nodes column, so the two columns are not consistent. Therefore,
nodes column will not be used for further analysis.

**Evaluate categorical variables**

```{r }
#| echo: true
#| message: false
 
summary_table <- colon_surv%>%summarise(count =n(),
                                        male = sum(sex), 
                                                       median_age = median(age),
                                                       ct_perforation = sum(perfor),
                                                       ct_adherence_nerby_organ = sum(adhere),
                                                       ct_death = sum(death))

summary_table
```

**Insight:** Total number of participants: 929. About half of the
participants are male and about half were censored, while the other half
died.

```{r}

colon_surv <- colon_surv%>%mutate(differentiation = case_when(differ == 1 ~ "well",
                                                              differ == 2 ~ "moderate",
                                                              differ == 3 ~ "poor"),
                                  local_spread = case_when(extent == 1 ~ "submucosa",
                                                           extent == 2 ~ "muscle",
                                                           extent == 3 ~ "serosa",
                                                           extent == 4 ~ "contiguous"),
                                  surg_to_reg_time = case_when(surg == 0~ "short",
                                                               surg == 1 ~ "long"))



```

**Frequency tables for categorical variables**

```{r}
#| warning: false

# frequency tables for categorical variables
# Tumor differentiation

colon_surv %>% 
  tabyl(differentiation, rx) %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 1) %>% 
  adorn_ns()

# extent of local spread
colon_surv %>% 
  tabyl(local_spread, rx) %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 1) %>% 
  adorn_ns()

# colum obstruction
colon_surv %>% 
  tabyl(obstruct, rx) %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 1) %>% 
  adorn_ns()


# colon perforation
colon_surv %>% 
  tabyl(perfor, rx) %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 1) %>% 
  adorn_ns()

# Adherance to nearby organs
colon_surv %>% 
  tabyl(adhere, rx) %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 1) %>% 
  adorn_ns()

# extent of local tumor spread
colon_surv %>% 
  tabyl(local_spread, rx) %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 1) %>% 
  adorn_ns()

# More than 4 lymph nodes with cancer
colon_surv %>% 
  tabyl(node4, rx) %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 1) %>% 
  adorn_ns()

# Recurrence
colon_surv %>% 
  tabyl(recurrence, rx) %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 1) %>% 
  adorn_ns()

colon_surv %>% 
  tabyl(recurrence, status) %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 1) %>% 
  adorn_ns()

# time from surgery to registration
colon_surv %>% 
  tabyl(surg, rx) %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 1) %>% 
  adorn_ns()
```

\
**Summary statistics grouped by treatment**

```{r #| echo: true#| message: false}

summary_table <- colon_surv%>%group_by(rx)%>%summarise(count =n(),
                                                       male = sum(sex),
                                                       median_age = median(age),
                                                       ct_perforation = sum(perfor),
                                                       ct_adherence_nerby_organ = sum(adhere),
                                                       ct_death = sum(death),
                                                       perc_male = (male/count)*100,
                                                       iqr_age = IQR(age))
summary_table

g <- colon_surv%>%filter(rx == "Lev+5FU")
summary(g$age)
```

**Insight:** Each treatment group had about 300 participants. Median
age, number of participants with perforation and adherence are similar
between the three groups. Whereas the total number of death are higher
in the Lev+5FU group.

## II. Table 1: Description of the study population

```{=html}
<style type="text/css">
.tg  {border-collapse:collapse;border-spacing:0;}
.tg td{border-color:black;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;
  overflow:hidden;padding:10px 5px;word-break:normal;}
.tg th{border-color:black;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;
  font-weight:normal;overflow:hidden;padding:10px 5px;word-break:normal;}
.tg .tg-bobw{font-weight:bold;text-align:center;vertical-align:bottom}
.tg .tg-7zrl{text-align:left;vertical-align:bottom}
.tg .tg-8d8j{text-align:center;vertical-align:bottom}
.tg .tg-j6zm{font-weight:bold;text-align:left;vertical-align:bottom}
</style>
```
+------------+------------+------------+------------+------------+
|            |            | O          | Amisole    | Amisole +  |
|            |            | bservation | (%)        | 5-FU (%)   |
|            |            | (%)        |            |            |
+============+============+============+============+============+
|            |            | N=315      | N=310      | N=304      |
+------------+------------+------------+------------+------------+
| D          |            |            |            |            |
| e          |            |            |            |            |
| mographics |            |            |            |            |
+------------+------------+------------+------------+------------+
|            | Male       | 166 (52.3) | 177 (57.1) | 141        |
+------------+------------+------------+------------+------------+
|            | Median age | 60         | 61         | 61         |
|            | (years)    | \[53,68\]  | \[53,69\]  | \[52,70\]  |
|            | \[IQR\]    |            |            |            |
+------------+------------+------------+------------+------------+
| Cancer cha |            |            |            |            |
| r          |            |            |            |            |
| acterstics |            |            |            |            |
+------------+------------+------------+------------+------------+
|            | Colon      | 63 (20.0)  | 63 (20.3)  | 54 (17.8)  |
|            | o          |            |            |            |
|            | bstruction |            |            |            |
+------------+------------+------------+------------+------------+
|            | Colon      | 9 (2.9)    | 10 (3.2)   | 8 (2.6)    |
|            | p          |            |            |            |
|            | erforation |            |            |            |
+------------+------------+------------+------------+------------+
|            | Adherence  | 47 (14.9)  | 49 (15.8)  | 39 (12.8)  |
|            | to nearby  |            |            |            |
|            | organs     |            |            |            |
+------------+------------+------------+------------+------------+
| Diff       |            |            |            |            |
| e          |            |            |            |            |
| rentiation |            |            |            |            |
| of tumor   |            |            |            |            |
+------------+------------+------------+------------+------------+
|            | Well       | 27 (8.6)   | 37 (11.9)  | 29 (9.5)   |
+------------+------------+------------+------------+------------+
|            | Moderate   | 236 (74.9) | 229 (73.9) | 221 (72.7) |
+------------+------------+------------+------------+------------+
|            | Poor       | 52 (16.5)  | 44 (14.2)  | 54 (17.8)  |
+------------+------------+------------+------------+------------+
| Extent of  |            |            |            |            |
| local      |            |            |            |            |
| spread     |            |            |            |            |
+------------+------------+------------+------------+------------+
|            | Contiguous | 20 (6.3)   | 12 (3.9)   | 11 (3.6)   |
+------------+------------+------------+------------+------------+
|            | Muscle     | 38 (12.1)  | 36 (11.6)  | 32 (10.5)  |
+------------+------------+------------+------------+------------+
|            | Serosa     | 249 (79.0) | 259 (83.5) | 251 (82.6) |
+------------+------------+------------+------------+------------+
|            | Submucosa  | 8 (2.5)    | 3 (1.0)    | 10 (3.3)   |
+------------+------------+------------+------------+------------+
| More than  | Yes        | 87 (27.6)  | 89 (28.7)  | 79 (26.0)  |
| 4 lymh     |            |            |            |            |
| nodes with |            |            |            |            |
| cancer     |            |            |            |            |
+------------+------------+------------+------------+------------+
| Recurrence | Yes        | 177 (56.2) | 172 (55.5) | 119 (39.1) |
| (%)        |            |            |            |            |
+------------+------------+------------+------------+------------+
| Short time | Yes        | 91 (28.9)  | 80 (25.8)  | 76 (25.0)  |
| from       |            |            |            |            |
| surgery to |            |            |            |            |
| r          |            |            |            |            |
| e          |            |            |            |            |
| gistration |            |            |            |            |
| (%)        |            |            |            |            |
+------------+------------+------------+------------+------------+

# III. Methods

The Cox proportional hazards model was used to model the relationship
between survival time and different lung cancer treatments. In
particlular the survival time will be compared between the untreated
group (observation) vs. those treated with amisole (Lev), or amisole +
5-FU. The Cox regression model was chosen for this study because it is
useful for studying association between survival time of patients and
predictors and allows estimating the relative risk or hazard ratios due
to the covariates, i.e., treatment status. The time (in days) until
event, i.e, death, will be modeled as a function of treatment and other
variables, including age, sex, and various tumor characteristics.
Significant predictors were included in the final model.

## Statistical analysis

The R statistical software version 4.3.2 [@R_citation] was used for all
analysis. The Survival package was used to construct the Cox regression
model [@survival-package] [@survival-book].

Cox regression model is based on the hazard function $h_x(t)$ with
covariates at time t given by:

$h_x(t)=h_0(t)\exp(\beta_1x_1 +\beta_2x_2 + \dots + \beta_p x_p)$

Where:

$h_x(t)$ is the hazard function

$h_0(t)$ is the baseline hazard function

$\beta_1x_1 + \beta_2x_2 + \dots +\beta_p x_p$ represent the linear
combination of covariates and their coefficient

The hazards for the observation vs. amisole (Lev), or amisole + 5-FU
group with covariate values x~1~ and x~2~ are given by:
$hx_1(t)=h_0(t)\exp(\beta_1x_1)$ and $hx_2(t)=h_0(t)\exp(\beta_2x_2)$,
respectively

The hazard ratio is expressed as: HR = $hx_2(t)$ / $hx_1(t)$ =
$\exp[\beta(x_2-x_1)]$

The Schoenfeld residual plot was constructed to test Cox proportional
hazards assumption. When the proportional hazards assumpiton was not met
for any of the covariates, stratification approach was explored. The
Survminer [@survminer] package was used to plot the Kaplan-Meier curve
to visualize the survival probability over time for each treatment
group.

Multicolinearity was tested using Variant Inflation Factor (VIF)
calculated using MASS package [@MASS].

The R MASS package was used for Stepwise model selection, using "both"
forward and backward variable selection [@MASS]. For Stepwise selection,
stepAIC() function uses AIC (Akaike Information Criterion) as the
measure to add or remove predictors from the model. Model performance
was evaluated using 100-fold cross-validation using the boot package
[@boot1] [@boot2].

# IV. Analysis: Cox regression model

#### Plot survival times

```{r}
#| echo: true
#| message: false
#| warning: false
# Create new incremental count id
colon_surv$idcount <- c(1:length(colon_surv$id))

# Order by survival time and create an order variable:
colon_surv <- colon_surv[order(-colon_surv$time, colon_surv$status),]
colon_surv$order <- c(1:length(colon_surv$idcount))

ggplot(data=colon_surv, aes(x=time, y=order)) +
geom_rect(xmin=23,xmax=colon_surv$time,ymin=colon_surv$order,ymax=colon_surv$order+1, colour="lightgray") +
geom_rect(xmin=colon_surv$time-2,xmax=colon_surv$time,ymin=colon_surv$order,ymax=colon_surv$order+1,
          fill=factor(colon_surv$status+1)) +
geom_vline(xintercept= 1976,linetype="solid") +
scale_x_continuous(breaks=seq(20,3330,650)) +
geom_text(aes(2600, 750, label="Median Survival Time")) +
xlab("Survival Time (Days)") + ylab("Participants (ordered by survival time)") +
ggtitle("Survival Times for Participant") +
theme_classic() +
theme(legend.position="none",
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
      panel.background=element_blank(),
      axis.line.x = element_line(color = "black"),
      axis.line.y = element_line(color = "black"))

```

#### Plot survival curve stratified by treatment group

```{r}
#| echo: true
#| message: false
#| warning: false

library(survminer)
library(survival)

fit <- survfit(Surv(time,status) ~ rx, data = colon_surv)
ggsurvplot(fit, data=colon_surv, risk.table = TRUE)

colon_surv%>%group_by(rx)%>%summarise(t= median(time))
```

**Insight:** The time for 50% Survival probability of the group treated
with Lev+5Fu is over 3000 days while the survival time for the
observation and Lev group is around 2000 days

#### Fit base Model

```{r}
m0 <- coxph(Surv(time, status) ~ 1, data = colon_surv)
summary(m0)
```

#### Perform cox regression to test whether treatment is significant predictor

```{r}

#| echo: true
#| message: false
#| warning: false

# Univariate analysis
m1 <- coxph(Surv(time, status) ~ rx, data = colon_surv)
summary(m1)



```

**Insight:** the coefficient of Lev is not significant, suggesting that
there is no evidence that this treatment affects survival time compared
to observation. however Lev+5Fu is significant (p=0.00175), indicating
that the treatment Lev +5Fu has a statistically significant effect on
survival time compared to the reference group. The negative sign
indicates that this treatment group has a lower hazard and likely a
longer survival time.

The hazard ratio for Lex+5FU (0.690), indicating the risk of death is
about 31% lower compared to the observation group.

The p-values indicate that the model is significant.

### Test the Cox proportional hazard assumption

```{r}

cox.zph(m1)
zph_test <- cox.zph(m1)

print(zph_test)

# plot the Schoenfeld residuals
plot(zph_test)

```

**Insight:** The Schoenfeld residal plot shows that the residuals are
scattered randomly and the smooth trend line is horizontal near 0. This
suggests that the hazard ratio for rx (treatment status) is constant
over time and the proportional hazard assumption is met. The global
p-value is \>0.05, indicating that the the assumption is met.

#### Perform multivariate analysis, including all variables to determine which predictors are significant.

```{r}
#| echo: true
#| message: false
#| warning: false

# Subset data for modeling
df <- colon_surv%>%dplyr::select(!c(id,study,etype,death,differ,recurrence, extent,surg_to_reg_time, idcount, order, nodes))

# multivariant analysis
m2 <- coxph(Surv(time, status) ~ rx+ age + sex + perfor + adhere + surg + obstruct + differentiation + node4+
              local_spread, data = df)  
summary(m2)


```

**Insight:** When all variables are included in the model, age,
obstruction, differentiation, and recurrence were significant predictor.
However, treatment is no longer significant.

#### Calculate Variance Inflation Factor (VIF) to assess multicollinearity among predictors

```{r}

vif <- vif(m2)
print(vif)
```

**Insight:** None of the variables have VIF values above 5, therefore
there is no multicollinearity

#### Variable selection method 1. Model survival while including different cancer characteristics as predictors separately to identify significance predictors.

```{r}

m2 <- coxph(Surv(time, status) ~ rx+ age + sex + perfor + adhere + surg + obstruct + differentiation + node4+
              local_spread, data = df)  

# Treatment
m2a <- coxph(Surv(time, status) ~ rx, data = colon_surv) # significant
summary(m2a)

# Demographics
m2b <- coxph(Surv(time, status) ~ age + sex, data = colon_surv) # not significant
summary(m2b)


# cancer characterstics
m2c <- coxph(Surv(time, status) ~ perfor + adhere + obstruct, data = colon_surv) # adhere and obstruct are significant
summary(m2c)

# Differentiation of tumor
m2d <- coxph(Surv(time, status) ~ differentiation, data = colon_surv) # significant
summary(m2d)

# Extent of local spread
m2f <- coxph(Surv(time, status) ~ local_spread, data = colon_surv) # significant
summary(m2f)

# Recurrence
# m2g <- coxph(Surv(time, status) ~ recurrence, data = colon_surv) # significant
# summary(m2g)

# short time from surgery to registration
m2h <- coxph(Surv(time, status) ~ surg, data = colon_surv) # significant
summary(m2h)


# include significant predictors in final model
model <- coxph(Surv(time, status) ~ rx + adhere + surg + obstruct + differentiation
              + local_spread, data = colon_surv)

summary(model)


```

### Test proportional hazard assumption for the model with significant predictors

```{R}
cox.zph(model)
zph_test <- cox.zph(m2)

print(zph_test)

# plot the Schoenfeld residuals
plot(zph_test)


```

**Insight:** Differentiation variable does not meet proportional hazards
assumption.

#### Variable selection method 2: Use the MASS package stepAIC() function for stepwise selection by using AIC (Akaike Information Criterion) as the measure to add or remove predictors from the model.

```{R}

library(MASS)       # for stepwise regression
library(boot)       # for cross-validation
```

### Perform Stepwise variable selection

```{R}

# stepwise selection
stepwise_model <- stepAIC(m2, direction = "both")

summary(stepwise_model)
```

```{r}

# FINAL MODEL

m2_select <- coxph(formula = Surv(time, status) ~ rx + age + surg + obstruct + 
    differentiation + node4 + local_spread, data = df)

summary(m2_select)

cox_summary <- tidy(m2_select)



```

### Cross-Validation for Model Evaluation

```{r}
#| echo: true
#| message: false
#| warning: false

# cross validation function
cv_cox <- function(data, indices) {
  # subset data
  d <- data[indices, ]
  
  # fit model on subset
  fit <- coxph(Surv(time, status) ~ rx + surg + obstruct + differentiation + node4 +
    local_spread, data = df)
  
  # return the concordance index (C-index)
  return(survConcordance(Surv(time, status) ~ predict(fit), data = d)$concordance)
}

# Set seed for reproducibility
set.seed(45)

# perform 100-fold cross-validation
cv_results <- boot(data = df, statistic = cv_cox, R = 100)

cv_results
```

### Visualization of cross-validation results: plot concordance index from bootstrap samples

```{R}
# Print summary of cross-validation results
median(cv_results$t)
# Visualize results

plot(cv_results)

```

**Insight:** The concordance index (c-index) of the original model
(0.67) is higher than the median bootstrap samples concordance (0.5),
suggesting overestimation of of model performance on the original
dataset. The model predictive power is not needs improvement based on
the c-index.

# V. Results

### Table 2. Unadjusted model: Survival after Chemotherapy for stage B/C Colon Cancer

+----------------+-------------+--------------+--------------+--------------+---------+
| Treatment      | Coefficient | Hazard ratio | 95% CI_upper | 95% CI_lower | P-value |
+================+=============+==============+==============+==============+=========+
| Amisole (Lev)  | -0.027      | 0.974        | 0.784        | 1.209        | 0.809   |
+----------------+-------------+--------------+--------------+--------------+---------+
| Amisole + 5-FU | -0.372      | 0.690        | 0.546        | 0.870        | 0.002   |
+----------------+-------------+--------------+--------------+--------------+---------+

### Table 3. Adjusted model: Survival after Chemotherapy for stage B/C Colon Cancer

+----------+----------+----------+----------+----------+----------+
| T        | Coe      | Hazard   | 95%      | 95%      | P-value  |
| reatment | fficient | ratio    | CI_upper | CI_lower |          |
+==========+==========+==========+==========+==========+==========+
| Amisole  | -0.011   | 0.989    | 0.795    | 1.231    | 0.923    |
| (Lev)    |          |          |          |          |          |
+----------+----------+----------+----------+----------+----------+
| A        | -0.376   | 0.687    | 0.543    | 0.868    | 0.002    |
| misole + |          |          |          |          |          |
| 5-FU     |          |          |          |          |          |
+----------+----------+----------+----------+----------+----------+
| Age      | 0.007    | 1.007    | 0.999    | 1.015    | 0.069    |
+----------+----------+----------+----------+----------+----------+
| Surge    | 0.244    | 1.276    | 1.042    | 1.562    | 0.018    |
+----------+----------+----------+----------+----------+----------+
| Obs      | 0.283    | 1.327    | 1.057    | 1.667    | 0.015    |
| truction |          |          |          |          |          |
| of colon |          |          |          |          |          |
+----------+----------+----------+----------+----------+----------+
| Diff     | 0.374    | 1.453    | 1.145    | 1.844    | 0.002    |
| erentiat |          |          |          |          |          |
| ion_poor |          |          |          |          |          |
+----------+----------+----------+----------+----------+----------+
| Diff     | 0.069    | 1.072    | 0.774    | 1.483    | 0.677    |
| erentiat |          |          |          |          |          |
| ion_well |          |          |          |          |          |
+----------+----------+----------+----------+----------+----------+
| More     | 0.930    | 2.534    | 2.089    | 3.074    | 3.745 x  |
| than 4   |          |          |          |          | 10\^21   |
| nodes    |          |          |          |          |          |
| (+)      |          |          |          |          |          |
+----------+----------+----------+----------+----------+----------+
| Local    | -0.996   | 0.370    | 0.225    | 0.606    | 7.849 x  |
| sprea    |          |          |          |          | 10\^5    |
| d_muscle |          |          |          |          |          |
+----------+----------+----------+----------+----------+----------+
| Local    | -0.501   | 0.606    | 0.414    | 0.886    | 0.010    |
| sprea    |          |          |          |          |          |
| d_serosa |          |          |          |          |          |
+----------+----------+----------+----------+----------+----------+
| Local    | -1.322   | 0.267    | 0.093    | 0.763    | 0.014    |
| spread_s |          |          |          |          |          |
| ubmucosa |          |          |          |          |          |
+----------+----------+----------+----------+----------+----------+
